Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source

### 2018-07-29 main.tex
updated ion formatting, other things in methods section

%mm \textit{Hydrodynamics ---} 
\paragraph{Hydrodynamics} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{} \citep{Enzo2014}. Hydrodynamics are solved using a direct-Eulerian piecewise parabolic method and a two-shock approximate Riemann solver with progressive fallback to more diffusive solvers. We include gas self-gravity and evolve collisionless star particles using a particle mesh N-body solver. We use a 128$^{3}$ base grid measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 8 levels of refinement, for a maximum spatial resolution of 1.8~pc. Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas 
%mm and 
    or
2) a cell's local Jeans length becomes resolved by less than eight cells. If the cell is within 4 zones of a star particle with active feedback, it is refined to the maximum resolution. At the maximum resolution, we use a pressure floor to prevent artificial fragmentation when the Jeans length is unresolved.

%mm \textit
\paragraph{Chemistry, Heating, and Cooling Physics} We use the the astrophysical chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (including molecular hydrogen), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}. We account for approximate self-shielding of HI against the UV background following \cite{Rahmati2013}. We assume HeI self-shields in the same fashion as HI, and ignore HeII heating from the UVB entirely. Approximate H$_2$ self-shielding from background Lyman-Werner (LW) radiation is accounted for using the Sobolov-like method from \cite{Wolcott-Green2011}. Finally, we use the updated metal line cooling tables which self-consistently account for the decrease in metal line cooling rates due to lower ionization fractions in self-shielding gas, as compared to metal cooling tables computed under the optically thin assumption.

@@

%mm \textit
\paragraph{Stellar Feedback and Stellar Yields} We track the feedback and yields of 15 metal species for each star individually. Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse supernovae at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution. Stars above this mass are assumed to direct collapse with no mass or energy injection. For all stars above 8~M$_{\odot}$ we follow their stellar winds assuming continuous mass loss over their lifetimes, their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively, and their HI and HeI ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}. We interpolate over the OSTAR2002 \citep{Lanz2003} grid to set the luminosities of each of these stars. Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind. Stars with $3 < M_{*,o} < 8$ are tracked after their death as possible Type Ia supernova progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields. Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, \textbf{Slemer et. al. in prep} for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia supernovae.

@@

The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain. We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow). Again, with the exception of H and He, we only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.

@@

% Classic chemical evolution models often adopt the simplifying assumption that metals from newly formed stars are instantly deposited back into the ISM \textbf{(examples)}. With added complication, this instantaneous recycling approximation (IRA) can be expanded upon by taking into account individual stellar lifetimes (references) which have been shown to produce significant variations in stellar abundances (references) as compared to IRA models. However, even in this new model it is unlikely that whatever fraction of a star's yields that remains in the ISM instantaneously enriches star forming gas. Rather, these yields are first injected through a hot phase (stellar winds, HII regions, supernovae), cooling over time into star forming gas. (refs for models accounting for this). We investigate this process in our simulations below, first by outlining a new analytic description of metal distributions in the ISM.

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{DD0390_element_by_element.png}
\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (blue), WNM (green), WIM (purple), HIM (red), and all the gas in the ISM (black). For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF. We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk. Since the CNM dominates the mass fraction of our galaxy, the black curve is often obscured at low metal fractions.}
\label{fig:log-normal}
\end{figure*}

@@

Unsurprisingly the diffuse HIM contains the most metal enriched gas, as it is comprised predominately of metal enriched supernova ejecta. Clearly this leads to long power-law tails towards high metal fractions for each species, with a very narrow, poorly defined peak at low metal fractions. Generally, in colder gas the metal PDFs become less enriched with broader low metal fraction components and steeper, power-law tails. Although the extended power-law tail of the HIM leads to a large range of metal fractions, the HIM represents very little mass, and this tail represents recent, un-mixed enrichment. The comparatively narrow width in the log-normal regimes of CNM is perhaps surprising. Although this gas is at lower metal fraction than the WNM and WIM, it would appear that it is more well mixed. This runs counter to the idea that mixing times should be long in colder gas unless mixing first proceeds rapidly in the hot phases before mixing in with cold, disconnected structures across the galaxy.

Although these trends across phases hold for all elements, there are qualitative differences between elements, particularly between those ejected predominantly by AGB winds (e.g. Ba and N) and those ejected by supernovae (e.g. O and Mg). In all phases, except the HIM, the AGB-wind elements have broader distributions that are less well described by our adopted $p(Z)$ than the metals dominated by supernova enrichment. The power-law component of N and Ba is generally shallower than all other metals across each phase (except the HIM), particularly in the CNM. Ba and N do not show significant differences among the rest of the metals in the HIM, though this is likely because the Ba and N present in this phase is dominated by the Ba and N produced in supernovae yields. Again these differences between yield sources could be driven both by differences in their enrichment timescales and therefore differences in the typical ISM environment each event encounters, and the differences in energetics between AGB winds and supernovae. AGB wind elements enrich the WNM and WIM directly, rather than the HIM, which would increase their mixing timescales and broaden their PDFs.

@@

For O, the median mass fraction is ordered by phase temperature. The HIM is significantly more enriched than the cooler phases by anywhere from 0.1 dex to 4 dex, fluctuating by $\pm$ 1 dex over the simulation time. The frequent large skew in the HIM (see second panel) and spread in the HIM (right two panels), coupled with its continual fluctuation, suggests that the HIM is not in equilibrium. 
%This phase is poorly mixed because it is short lived, either cooling into different phases of the ISM or being ejected from the galaxy, and is continually enriched by new SN events. 
Each cooler phase in O is progressively less enriched (lower median), with smaller skew and spread. The offset between phases and increasingly well mixed gas from hot to cold indicates that metal enrichment in the ISM of galaxies proceeds first through mixing on large scales in a hot phase, before progressively cooling through multiple phases until enriching star forming gas. This is the only explanation for how the cold gas can rapidly homogenize over the whole galaxy within $\sim$50 Myr, roughly when the cold phase exhibits a nearly constant spread (right panels). Individual enrichment events will have significantly higher metallicities than the ambient ISM in any phase, and will drive an increase in the difference between the mean and median of the PDF. These can be seen as the obvious spikes in the HIM and WIM. For O, the lack of these spikes in the two cold phases suggests again that enrichment does not occur directly in these phases, but proceeds more gradually through the warmer phases first.

@@

Although these trends are generally true for Ba, its evolution is much more complicated.
%In addition, the HIM is much less offset from the rest of the phases than is seen in O, with much less variability. 
Unlike O, the spread and skew in Ba for the CNM, WNM, and WIM \textit{increase} in during the evolution, reaching differences in 90$^{\rm th}$ and 10$^{\rm th}$ percentiles of nearly 2 dex in the CNM and over 2 dex in the WNM and WIM. The HIM is seemingly unaffected by this trend, and simply fluctuates throughout the simulation. Given their lower energies, AGB winds more directly enrich the WNM and WIM, not the HIM as in supernovae. The consequence of this is clear in Figure~\ref{fig:log-normal} by the wider PDFs and longer power-law tails in Ba in these phases. These tails represent the most recently enriched gas, and is clearly much more locally confined than O.

@@

To summarize, this figure demonstrates: 1) there are qualitative differences in how supernova injected elements (e.g. O, Mg) and AGB wind injected elements (e.g. N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the HIM, 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM, and the hotter phases are more directly populated by recent enrichment events, 3) the cooler, denser phases, particularly for supernova injected elements, are more well mixed than the hot phases of the ISM, 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function, and therefore 5) the median metallicity available for star formation rates lies below the mean galactic value. In the case of supernova injected elements, enrichment proceeds quickly through the HIM over the entire galaxy. For AGB injected elements, enrichment proceeds through the WIM and WNM, leading to longer mixing timescales and larger metal fraction variations in the ISM.

@@

This toy model provides a physical intuition for the general trends in the PDFs presented here across ISM phases. The HIM is comprised predominantly of gas from individual enrichment events that, due to its low density, easily create large power-law tails beginning at very high metal fractions. Whatever ambient component of the HIM that exists is well mixed, leading to a narrow and sub-dominant log-normal component at low-metallicities. Cold, dense gas, which is almost never directly impacted by these individual enrichment events, is enriched almost entirely by diffusion, and thus has an almost completely log-normal PDF with very little, if any, power-law tail.

@@

%
% A.E. paragraph may need work
%
Mixing timescales are likely proportional to the eddy turnover times at the injection scale \citep{PanScannapieco2010, Colbrook2017} and the properties of turbulence in the ISM \citep{YangKrumholz2012}. Mixing within a phase is likely dependent upon the phase's sound speed and velocity dispersion. This would imply rapid mixing timescales in the WIM and HIM, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in cold, dnese gas ($\sim$ 1 km s$^{-1}$). Our results show, however, that in general the WIM and HIM are the least well mixed, while the CNM is the most well mixed across the galaxy. This is particularly curious as the sound crossing time of the HIM across the galaxy ($\sim 1$ kpc) is $\sim$10~Myr, compared to $\sim$~1~Gyr for the coldest gas. It must be that the HIM is far from equillibrium throughout the simulation, in part due to the continual enrichment by ongoing supernovae. Newly enriched gas must mix through the HIM on galaxy scales, becoming well mixed and less enriched by the time it cools into the CNM and eventually star forming gas. Since elements produced in AGB winds do not directly enter the HIM, mixing is less efficient driving larger variations across the galaxy. The idea of metals processing first through the hot ISM has been proposed before to explain observed metallicity trends in the outskirts of more massive galaxies \citep{Tassis2008,Werk2011}.

@@

%We discuss possible caveats to this in Section~\ref{sec:caveats}. Does this extend to more massive? how does DM potential affect this? Are general trends still true in much larger galaxies? or are things very different once HIM crossing times are more like 100 Myr (aka MW size galaxies).

>>>>

%mm \textit{Hydrodynamics ---} 
\paragraph{Hydrodynamics} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{} \citep{Enzo2014}. Hydrodynamics are solved using a direct-Eulerian piecewise parabolic method and a two-shock approximate Riemann solver with progressive fallback to more diffusive solvers. We include gas self-gravity and evolve collisionless star particles using a particle mesh N-body solver. We use a 128$^{3}$ base grid measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 8 levels of refinement, for a maximum spatial resolution of 1.8~pc. Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas 
%mm and 
    or
2) a cell's local Jeans length becomes resolved by less than eight cells. Also, if the cell is within four zones of a star particle with active feedback, it is refined to the maximum resolution. At the maximum resolution, we use a pressure floor to prevent artificial fragmentation when the Jeans length is unresolved.

%mm \textit
\paragraph{Chemistry, Heating, and Cooling Physics} We use the the astrophysical chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (including molecular hydrogen), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}. We account for approximate self-shielding of H~{\sc i} against the UV background following \cite{Rahmati2013}. We assume He~{\sc i} self-shields in the same fashion as H~{\sc i}, and ignore He~{sc ii} heating from the UVB entirely. Approximate H$_2$ self-shielding from background Lyman-Werner (LW) radiation is accounted for using the Sobolov-like method from \cite{Wolcott-Green2011}. Finally, we use the updated metal line cooling tables which self-consistently account for the decrease in metal line cooling rates due to lower ionization fractions in self-shielding gas, as compared to metal cooling tables computed under the optically thin assumption.

@@

%mm \textit
\paragraph{Stellar Feedback and Stellar Yields} We track the feedback and yields of 15 metal species for each star individually. Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse supernovae at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution. Stars above this mass are assumed to direct collapse with no mass or energy injection. For all stars above 8~M$_{\odot}$ we follow their stellar winds assuming continuous mass loss over their lifetimes, their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively, and their H~{\sc i} and He~{\sc i} ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}. We interpolate over the OSTAR2002 \citep{Lanz2003} grid to set the luminosities of each of these stars. Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind. Stars with $3 < M_{*,o} < 8$ are tracked after their death as possible Type Ia supernova progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields. Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, \textbf{Slemer et. al. in prep} for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia supernovae.

@@

The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain. We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (H~{\sc i}M T$\ge 10^{5.5}$~K), and locked in stars (yellow). Again, with the exception of H and He, we only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.

@@

% Classic chemical evolution models often adopt the simplifying assumption that metals from newly formed stars are instantly deposited back into the ISM \textbf{(examples)}. With added complication, this instantaneous recycling approximation (IRA) can be expanded upon by taking into account individual stellar lifetimes (references) which have been shown to produce significant variations in stellar abundances (references) as compared to IRA models. However, even in this new model it is unlikely that whatever fraction of a star's yields that remains in the ISM instantaneously enriches star forming gas. Rather, these yields are first injected through a hot phase (stellar winds, H~{\sc ii} regions, supernovae), cooling over time into star forming gas. (refs for models accounting for this). We investigate this process in our simulations below, first by outlining a new analytic description of metal distributions in the ISM.

@@

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{DD0390_element_by_element.png}
\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (blue), WNM (green), WIM (purple), H~{\sc i}M (red), and all the gas in the ISM (black). For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF. We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk. Since the CNM dominates the mass fraction of our galaxy, the black curve is often obscured at low metal fractions.}
\label{fig:log-normal}
\end{figure*}

@@

Unsurprisingly the diffuse H~{\sc i}M contains the most metal enriched gas, as it is comprised predominately of metal enriched supernova ejecta. Clearly this leads to long power-law tails towards high metal fractions for each species, with a very narrow, poorly defined peak at low metal fractions. Generally, in colder gas the metal PDFs become less enriched with broader low metal fraction components and steeper, power-law tails. Although the extended power-law tail of the H~{\sc i}M leads to a large range of metal fractions, the H~{\sc i}M represents very little mass, and this tail represents recent, un-mixed enrichment. The comparatively narrow width in the log-normal regimes of CNM is perhaps surprising. Although this gas is at lower metal fraction than the WNM and WIM, it would appear that it is more well mixed. This runs counter to the idea that mixing times should be long in colder gas unless mixing first proceeds rapidly in the hot phases before mixing in with cold, disconnected structures across the galaxy.

Although these trends across phases hold for all elements, there are qualitative differences between elements, particularly between those ejected predominantly by AGB winds (e.g. Ba and N) and those ejected by supernovae (e.g. O and Mg). In all phases, except the H~{\sc i}M, the AGB-wind elements have broader distributions that are less well described by our adopted $p(Z)$ than the metals dominated by supernova enrichment. The power-law component of N and Ba is generally shallower than all other metals across each phase (except the H~{\sc i}M), particularly in the CNM. Ba and N do not show significant differences among the rest of the metals in the H~{\sc i}M, though this is likely because the Ba and N present in this phase is dominated by the Ba and N produced in supernovae yields. Again these differences between yield sources could be driven both by differences in their enrichment timescales and therefore differences in the typical ISM environment each event encounters, and the differences in energetics between AGB winds and supernovae. AGB wind elements enrich the WNM and WIM directly, rather than the H~{\sc i}M, which would increase their mixing timescales and broaden their PDFs.

@@

For O, the median mass fraction is ordered by phase temperature. The H~{\sc i}M is significantly more enriched than the cooler phases by anywhere from 0.1 dex to 4 dex, fluctuating by $\pm$ 1 dex over the simulation time. The frequent large skew in the H~{\sc i}M (see second panel) and spread in the H~{\sc i}M (right two panels), coupled with its continual fluctuation, suggests that the H~{\sc i}M is not in equilibrium. 
%This phase is poorly mixed because it is short lived, either cooling into different phases of the ISM or being ejected from the galaxy, and is continually enriched by new SN events. 
Each cooler phase in O is progressively less enriched (lower median), with smaller skew and spread. The offset between phases and increasingly well mixed gas from hot to cold indicates that metal enrichment in the ISM of galaxies proceeds first through mixing on large scales in a hot phase, before progressively cooling through multiple phases until enriching star forming gas. This is the only explanation for how the cold gas can rapidly homogenize over the whole galaxy within $\sim$50 Myr, roughly when the cold phase exhibits a nearly constant spread (right panels). Individual enrichment events will have significantly higher metallicities than the ambient ISM in any phase, and will drive an increase in the difference between the mean and median of the PDF. These can be seen as the obvious spikes in the H~{\sc i}M and WIM. For O, the lack of these spikes in the two cold phases suggests again that enrichment does not occur directly in these phases, but proceeds more gradually through the warmer phases first.

@@

Although these trends are generally true for Ba, its evolution is much more complicated.
%In addition, the H~{\sc i}M is much less offset from the rest of the phases than is seen in O, with much less variability. 
Unlike O, the spread and skew in Ba for the CNM, WNM, and WIM \textit{increase} in during the evolution, reaching differences in 90$^{\rm th}$ and 10$^{\rm th}$ percentiles of nearly 2 dex in the CNM and over 2 dex in the WNM and WIM. The H~{\sc i}M is seemingly unaffected by this trend, and simply fluctuates throughout the simulation. Given their lower energies, AGB winds more directly enrich the WNM and WIM, not the H~{\sc i}M as in supernovae. The consequence of this is clear in Figure~\ref{fig:log-normal} by the wider PDFs and longer power-law tails in Ba in these phases. These tails represent the most recently enriched gas, and is clearly much more locally confined than O.

@@

To summarize, this figure demonstrates: 1) there are qualitative differences in how supernova injected elements (e.g. O, Mg) and AGB wind injected elements (e.g. N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the H~{\sc i}M, 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM, and the hotter phases are more directly populated by recent enrichment events, 3) the cooler, denser phases, particularly for supernova injected elements, are more well mixed than the hot phases of the ISM, 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function, and therefore 5) the median metallicity available for star formation rates lies below the mean galactic value. In the case of supernova injected elements, enrichment proceeds quickly through the H~{\sc i}M over the entire galaxy. For AGB injected elements, enrichment proceeds through the WIM and WNM, leading to longer mixing timescales and larger metal fraction variations in the ISM.

@@

This toy model provides a physical intuition for the general trends in the PDFs presented here across ISM phases. The H~{\sc i}M is comprised predominantly of gas from individual enrichment events that, due to its low density, easily create large power-law tails beginning at very high metal fractions. Whatever ambient component of the H~{\sc i}M that exists is well mixed, leading to a narrow and sub-dominant log-normal component at low-metallicities. Cold, dense gas, which is almost never directly impacted by these individual enrichment events, is enriched almost entirely by diffusion, and thus has an almost completely log-normal PDF with very little, if any, power-law tail.

@@

%
% A.E. paragraph may need work
%
Mixing timescales are likely proportional to the eddy turnover times at the injection scale \citep{PanScannapieco2010, Colbrook2017} and the properties of turbulence in the ISM \citep{YangKrumholz2012}. Mixing within a phase is likely dependent upon the phase's sound speed and velocity dispersion. This would imply rapid mixing timescales in the WIM and H~{\sc i}M, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in cold, dnese gas ($\sim$ 1 km s$^{-1}$). Our results show, however, that in general the WIM and H~{\sc i}M are the least well mixed, while the CNM is the most well mixed across the galaxy. This is particularly curious as the sound crossing time of the H~{\sc i}M across the galaxy ($\sim 1$ kpc) is $\sim$10~Myr, compared to $\sim$~1~Gyr for the coldest gas. It must be that the H~{\sc i}M is far from equillibrium throughout the simulation, in part due to the continual enrichment by ongoing supernovae. Newly enriched gas must mix through the H~{\sc i}M on galaxy scales, becoming well mixed and less enriched by the time it cools into the CNM and eventually star forming gas. Since elements produced in AGB winds do not directly enter the H~{\sc i}M, mixing is less efficient driving larger variations across the galaxy. The idea of metals processing first through the hot ISM has been proposed before to explain observed metallicity trends in the outskirts of more massive galaxies \citep{Tassis2008,Werk2011}.

@@

%We discuss possible caveats to this in Section~\ref{sec:caveats}. Does this extend to more massive? how does DM potential affect this? Are general trends still true in much larger galaxies? or are things very different once H~{\sc i}M crossing times are more like 100 Myr (aka MW size galaxies).
